Enabling GPU Virtualization in Cloud Environments

### 2015-10-23 paper.tex
revisión 5.4

\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE.]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE.]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE.]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{Different configurations where an AWS instance acting as a client is using several remote GPUs.}
\label{fig:aws}
\end{figure*}

@@

\subsection{Discussion}
Putting all together,  it is crystal clear that the AWS GPU-instances are not aimed to HPC because neither the network nor the accelerators are powerful enough to reach an appropriate performance
while running intensive parallel applications. 
Hence, AWS's target is more oriented to offer the service than to provide performance.
Also with the aim of plainly offering the service of GPGPU, AWS lacks in flexibility. 
AWS forces the user to choose between a basic instance with a GPU and a powerful instance with 4 GPUs.

Coming back to the Table~\ref{table:awsInstances} can be seen how not only the resources of the ``g2.8xlarge'' has been quadrupled, but also the cost per hour.
So, in the case of having other necessities (talking in terms of the instances type), with remotes GPUs we could attach an accelerator to any kind of instance.
Furthermore, reducing the budget in VM could be possible by customizing the resources of the available instances.
If needed, we could work on an instance of 2 GPUs for only \$ 1.3 by launching 2 ``g2.2xlarge'' and using remote GPUs. 
Avoiding to pay the double for features that we are not willing to use in ``g2.8xlarge''.

The last conclusion we will draw is related to GPU-shareability. 
As we deduced, AWS has GPU-capable physical machines reserved which could be idle until a GPU-instance request were made.
To have such an expensive accelerators in a standby state is counter-productive. So, it would make more sense if we had less devices, accessible from any machine, though.

>>>>

\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE.]{%
\includegraphics[width=0.315\linewidth]{images/aws3.pdf}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE.]{%
\includegraphics[width=0.315\linewidth]{images/aws2.pdf}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE.]{%
\includegraphics[width=0.315\linewidth]{images/aws1.pdf}
\label{subfig:aws3}}
\caption{Configurations where an AWS instance, acting as a client, employs several remote GPUs.}
\label{fig:aws}
\end{figure*}

@@

\subsection{Discussion}
The previous experiments reveal that the AWS GPU-instances are not appropriate for HPC
because neither the network nor the accelerators are powerful enough to deliver high performance
when running compute-intensive parallel applications. 
In other words, AWS is more oriented to offer service than to provide performance.
Also, AWS aims to offer a GPGPU service but fails in offering flexibility.
Concretely, AWS forces the user to choose between a basic instance with a GPU and a powerful instance with 4 GPUs.

Table~\ref{table:awsInstances} shows that the resources of the ``g2.8xlarge'' are quadrupled, but so is the cost per hour.
Therefore, in the case of having other necessities (in terms of the instances type), with GPU virtualization technology we could attach an accelerator to any kind of instance.
Furthermore, reducing the budget destinated to cloud services could be possible by customizing the resources of the available instances.
For example, we can work on an instance with 2 GPUs for only \$ 1.3 by launching 2 ``g2.2xlarge'' and using remote GPUs, avoiding to pay the double for features that we are not willing to use in ``g2.8xlarge''.

The last conclusion is related to GPU-shareability. 
As we deduced, AWS reserves GPU-capable physical machines which will be idle until a GPU-instance request is made.
To maintain an expensive accelerator in a standby state is counter-productive. 
It makes more sense to dedicate less devices, accessible from any machine.
